On the 3-cycle of the logistic map

### 2013-04-19 doc/p3p.tex
cobweb.gp oddcycls.gp: nicer arrows and colors
small HTML modifications

%\documentclass[12pt]{article}
\documentclass[twocolumn,prl]{revtex4-1}
\usepackage{amsmath}

\begin{document}
\title{On the 3-cycle of the logistic map}
\author{Cheng Zhang}
\date{April 17, 2013}
\begin{abstract}
We review a simple derivation of
  the onset and bifurcation points the 3-cycle
  of the logistic map.
\end{abstract}
\maketitle

%\section{Introduction}
The logistic map is defined as
\[
  z_{n+1} = F(z_n) = r z_n (1 - z_n).
\]
We want to find what $r$ values permit a \emph{stable} 3-cycle,
i.e., a solution of $z_{n+3} = z_n$,
which can sustain a small deviation in the initial $z_0$.
The two boundaries $r_0$ and $r_1$
  of the stable window $(r_0, r_1)$
  are called the \emph{onset} and \emph{bifurcation} points, respectively.
%
By a change of variables
\begin{equation}
  x_n = r (z_n - 1/2),
  R = (r^2 - 2 r)/4,
\label{eq:chvars}
\end{equation}
we get a simplified map
\[
x_{n+1} = f(x_n) = R - {x_n}^2.
\]
The onset and bifurcation points will be solved
  in terms of $R$, and the corresponding $r$ values
  are obtained by (\ref{eq:chvars}).

@@

Let $a$, $b$ and $c$ be the three points in the 3-cycle:
\begin{equation}
  b=f(a), c=f(b), a=f(c).
\label{eq:abc}
\end{equation}
We define the cyclic polynomials
$X = a+b+c$,
$X_k = a^k+b^k+c^k$ (for $k = 2,3$),
$Y = ab+bc+ca$, and $Z = abc$.
We will show that the equations of $X$, $X_k$, $Y$, and $Z$
are helpful in determining the two points of the 3-cycle.

>>>>

%\documentclass[12pt]{article}
\documentclass[twocolumn,prl]{revtex4-1}
\usepackage{amsmath}
\usepackage{times}

\begin{document}
\title{On the 3-cycle of the logistic map}
\author{Cheng Zhang}
\date{April 17, 2013}

\begin{abstract}
We review a simple derivation of
  the onset and bifurcation points the 3-cycle
  of the logistic map.
\end{abstract}
\maketitle

%\section{Introduction}
The logistic map is defined as
\[
  z_{n+1} = F(z_n) = r z_n (1 - z_n).
\]
We want to find the $r$ values that permit a \emph{stable} 3-cycle,
i.e., a solution of $z_{n+3} = z_n$,
which can sustain a small deviation in the initial $z_0$.
The two boundaries $r_0$ and $r_1$
  of the stable window $(r_0, r_1)$
  are called the \emph{onset} and \emph{bifurcation} points, respectively.
%
By a change of variables
\begin{equation}
  x_n = r (z_n - 1/2),
  R = (r^2 - 2 r)/4,
\label{eq:chvars}
\end{equation}
we get a simplified map
\[
x_{n+1} = f(x_n) = R - {x_n}^2.
\]
The onset and bifurcation points will be solved
  in terms of $R$, and the corresponding $r$ values
  are obtained by (\ref{eq:chvars}).

@@

Let $a$, $b$ and $c$ be the three points in the 3-cycle:
\begin{equation}
  b=f(a), c=f(b), a=f(c).
\label{eq:abc}
\end{equation}
We define the cyclic polynomials
$X = a+b+c$,
$X_k = a^k+b^k+c^k$ (for $k = 2,3$),
$Y = ab+bc+ca$, and $Z = abc$.
The equations of $X$, $X_k$, $Y$, and $Z$
are more helpful than those of $a$, $b$ and $c$
in determining the two points of the 3-cycle.
